Contextual Combinatorial Cascading Bandits

### 2016-01-31 contextual combinatorial cascading bandits.tex
update discussion and conclusion

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
%\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
\usepackage[accepted]{icml2016}

@@

%Stochastic online learning with combinatorial actions has been studied with semi-bandit feedback \cite{chen2013combinatorial}.

@@

Our setting generalizes several existing works but not limited to them.
If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in

in medical treatment, a patient will be recommended with a series of treatments. The patient has to take the treatments one by one, so the series of treatment actually is a list. Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$. $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment. We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$. So a treatment $a$ is successful with probability
\begin{equation}
\label{eq:betaTau}
1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
\end{equation}
where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number. We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful. So the expected reward function is
$$
f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
$$
where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.

By the expression of $f$, it is a function of the expected reward $w$. Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$. Therefore, the expected reward has the property of monotonicity. For the Lipschitz continuity, by the Lipschitz continuity of expected reward function with conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.

Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives. Similarly, there exists a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.

@@

\subsection{Synthetic}
\label{sec:ExpSyn}

@@

\subsection{MovieLens}

@@

\subsection{Network Routing}

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, a class of contextual combinatorial bandits with partial observations.

>>>>

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}

@@

@@

Our setting generalizes several existing works but does not limit to them. Consider in network routing problem, the observed information would be the latency on specific edges. The latency, or {\it weight}, on an edge is an exponential variable with mean $\theta_{\ast}^{\top}x$. Suppose we treat an edge as blocked if the latency on it is larger than some tolerance $\tau$. And we wait the edge to respond for at most $2\tau$ time. Then the real observed latency is new random variable from a cut-off exponential distribution with mean $\theta_{\ast}^{\top}x$. Then the edge is unblocked, or with reward $1$, if the new random vairable is less than the tolerance $\tau$ and the expectation is a function, say $g$, of $\theta_{\ast}^{\top}x$. It is not difficult to check that $g$ satisfies the properties of monotonicity and Lipschitz continuity. And the expected reward of a path is a composition of the expected reward function of conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the function $g$. (In original formulation, $g$ is the identity function, where $g(w) = w$.) Such an expected reward function satisfies the properties of monotonicity and Lipschitz continuity and can not be represented in conjunctive/disjunctive objectives, like in \cite{kveton2015cascading,kveton2015combinatorial}.

%Our setting generalizes several existing works but not limited to them. If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in

%in medical treatment, a patient will be recommended with a series of treatments. The patient has to take the treatments one by one, so the series of treatment actually is a list. Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$. $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment. We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$. So a treatment $a$ is successful with probability
% \begin{equation}
% \label{eq:betaTau}
% 1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
% \end{equation}
% where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number. We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful. So the expected reward function is
% $$
% f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
% $$
% where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.

%By the expression of $f$, it is a function of the expected reward $w$. Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$. Therefore, the expected reward has the property of monotonicity. For the Lipschitz continuity, by the Lipschitz continuity of expected reward function with conjunctive objective, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.

%Thus this expected reward function satisfies our setting but can not be fit into previous works, that is, can not be represented by the reward functions with disjunctive/conjunctive objectives. Similarly, there exists a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.

@@

\subsection{Synthetic Data}
\label{sec:ExpSyn}

@@

\subsection{MovieLens Data}

@@

\subsection{Network Routing Data}

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action can be observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve context information and position discounts. In the next, we want to derive a lower bound for this problem.
